Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
wip

\subsection{Threat Model and Limitations}

@@

\section{Building a Property}
\label{sec:ideas}

>>>>

\subsection{Threat Model and Limitations}
\apt{This could probably go better at end of next section.}

@@

\section{Framework}
\label{sec:ideas}

Our properties are

We assume a conventional hardware ISA, such as x86-64, ARM, or RISC-V, with a program counter and stack pointer,
and a standard ABI with a contiguous stack that holds interleaved data and control information.
The machine might be enhanced with additional monitoring or other security mechanisms,
such as hardware tags or capabilities. We do not , but....
